Automated topic naming to support analysis of software maintenance activities

### 2010-08-18 icse/icse2011.tex
minor change to remove old figure
updated the table.. but unsure

\todo[inline,color=green]{this table should have mysql}
\begin{table}
	\centering
\begin{tabular}{c|c|c|c}
\toprule
Measure & \textsf{exp1} & \textsf{exp2} & \textsf{exp3} \\
\midrule
Named topics   & 281 & 125 & 328  \\
Unnamed topics & 139 & 295 & 92   \\
\bottomrule
\end{tabular}
	\caption{Automatic topic labelling for MaxDB 7.500}
	\label{tbl:wordlist}

@@

\begin{figure*}%[h]
  \centering
 %\includegraphics[width=.97\textwidth]{mysql-time-smear-plot-Equal}
  %\includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
  \includegraphics[width=.97\textwidth]{figures/mysql-timeline}
  \caption{MySQL 3.23: NFRs over time. Topic frequency relative to that quality is mapped to alpha (transparency) value.}
  \label{fig:mysql}
\end{figure*}

>>>>

%\todo[inline,color=green]{this table should have mysql}
\begin{table}
% This data came from running  
%   python check_validity.py
%  in src/validate
% and then running
% tail -n 5 *maxdb*yes_no*
% tail -n 5 *mysql*yes_no*
	\centering
\begin{tabular}{c|c|c|c}
\toprule
Project & Measure & \textsf{exp1} & \textsf{exp2} & \textsf{exp3} \\
\midrule
%Named topics   & 281 & 125 & 328  \\
%Unnamed topics & 139 & 295 & 92   \\
MaxDB 7.500 & Named Topics   & 305 & 183 & 330 \\
MaxDB 7.500 & Unnamed Topics & 84  & 206 & 59   \\
MaxDB 7.500 & Total  Topics  & 389 & 389 & 389 \\
MySQL 3.23  & Named Topics   & 341 & 202 & 469 \\
MySQL 3.23  & Unnamed Topics & 245 & 384 & 117 \\
MySQL 3.23  & Total  Topics  & 586 & 586 & 586 \\
\bottomrule
\end{tabular}
	\caption{Automatic topic labelling for MaxDB 7.500}
	\label{tbl:wordlist}

@@

\begin{figure*}%[h]
  \centering
 %\includegraphics[width=.97\textwidth]{mysql-time-smear-plot-Equal}
  %\includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
  \includegraphics[width=\textwidth]{figures/mysql-timeline}
  \caption{MySQL 3.23: NFRs over time. Topic frequency relative to that quality is mapped to alpha (transparency) value.}
  \label{fig:mysql}
\end{figure*}
